Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-22 lqg-strings.tex
Added Derek Wise reference, todolist, logical chain of thought leading to this picture.

@@

\subsection{}\label{sec:}

\section{Physical Implications}

>>>>

\textbf{todo:}

\begin{itemize}
	\item Describe iso(d,1) connection decomposition into Lorentz piece and translation piece using \cite{Wise2010MacDowell-Mansouri} as reference.
	\item Explain why deSitter, anti-deSitter and flat space are the only consistent solutions for the enlarged bulk geometry.
	\item Recall once again the steps which led us here. 
\end{itemize}

\textbf{Steps which led us here}

\begin{itemize}
	\item We adopt the central result of LQG which is quantization of area
	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.
	\item Connection variables are used in LQG to describe geometry. So we should search for non-metrical description of coupling string geometry to bulk.
	\item For arbitrarily curved bulk geometry, global Poincare symmetry of embedding fields is meaningless.
	\item Elevate global Poincare to local Poincare following the lessons of gauge theory, which leads to introduction of extra "holographic" co-ordinate.
	\item Investigate physical implications of holographic co-ordinate for string phenomenology in this picture.
\end{itemize}

@@
